% Document structure and styling
\input{structure.tex}

\begin{document}
\input{header}

\cat{Education}

\new{2020 -- Present}
{B.Sc Programming and Data Science}
{Indian Institute of Technology (IIT)}
{Madras, IN}

\textbf{Specialization:}
Machine Learning and Artificial Intelligence

\new{2016 -- 2019}
{B.Sc Physics Chemistry Mathematics}
{Christ University}
{Bangalore, IN}

CGPA: 3.14/4.00
\medskip

\textbf{Discipline-Specific Electives}\\
Physics: Analog and Digital Electronics, Quantum Mechanics\\
Mathematics: Calculus of several variables, Graph Theory
\medskip

\textbf{Generic Electives}\\
Teaching Learning\\
Astronomy and Astrophysics\\
Health and Psycho-Physiology

\cat{Research Experience}

\new{Aug 2019 -- Oct 2019}
{Visiting Student Program (VSP)}
{Raman Research Institute}
{Bangalore, IN}

In this project, I worked closely with Prof. Avinash Deshpande to find out probability distributions associated with maximum entropy. With constraints on standard deviation, variance, etc. Entropy equations used here are different from that of Shannon's.

\new{Apr 2018 -- May 2018}
{Summer Research Project}
{Kerala School of Mathematics}
{Kozhikode, IN}

Explored Elliptic functions, Discriminant delta function, Dedekind eta function, and Ramanujan’s tau function under the guidance of the Number theorist Prof. M Manickam.

\new{Apr 2017 -- May 2017}
{Visiting Student Research Program (VSRP)}
{TIFR - Centre for Applicable Mathematics}
{Bangalore, IN}

Explored ideas of Metric space and Real analysis with Prof. KT Joseph. Attempted to understand Why Mathematics is called the language of Nature.
\newpage
\cat{Work Experience}

\new{Feb 2020 -- Mar 2020}
{Research and Development Intern}
{Sciensation Society}
{Hyderabad, IN}

Designed and Developed Student-centered Curriculum using Design Thinking approach based on Research, and Philosophy of Science and Language.

\cat{Honors and Awards}

\new{Mar 2014}
{Junior Mathematical Olympiad}
{Kendriya Vidyalaya Sangathan}
{New Delhi, IN}

All India Rank: 29

\new{Sep 2014, 2013}
{Painting Competition}
{Kerala House}
{New Delhi, IN}

Position: First
\cat{Workshops and Seminars}

\new{Oct 2019}
{Manim (Python library for Mathematics Animation)}
{Indian Institute of Science}
{Bangalore, IN}

\new{May 2018}
{Number Theory and Algebra}
{Kerala School of Mathematics}
{Kozhikode, IN}

\new{Mar 2018}
{Python Programming}
{Christ University}
{Bangalore, IN}

\new{Feb 2018}
{Mathematical Analysis}
{Christ University}
{Bangalore, IN}

\new{Nov 2017}
{Amateur Radio}
{Indian Institute of Hams}
{Bangalore, IN}

\new{Feb 2017}
{Stellar Astrophysics}
{Christ University}
{Bangalore, IN}

\cat{Skills}
\bigskip

\sky{Languages}
{English (Fluent), Malayalam (Native), Hindi (Fluent)}

\sky{Programming}
{Python (Intermediate), C++ (Advanced), Linux (Intermediate)}

Scripting \& Automation using command-line Linux programs

\sky{Markup}
{LaTeX (Advanced), HTML-CSS (Intermediate)}

% Set PDF meta-information
\hypersetup{
	pdftitle={Albert Shaji - Curriculum vitae},
	pdfauthor={Albert Shaji}
}
\end{document}
